Wigglyhedra

### 2024-07-08 draft/wigglyhedra.tex
change g- to \b{g}-

Recall from~\cref{rem:incompatibility-deg} that two arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.
Recall from~\cref{prop:uerp} the arcs \(\beta\) and \(\beta'\) associated to \(\alpha\) and \(\alpha'\).
Finally, recall from~\cref{lem:linearDependences} that the \(g\)-vectors of the arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
Let us interpret this dependince categorically.

Let \(X\) and \(X'\) be spherical objects in the standard heart that correspond to \(\alpha\) and \(\alpha'\) respectively.
First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial extension between the corresponding objects of the standard heart.
Next, let us understand~\(\beta\) and \(\beta'\) categorically.
\begin{proposition}\label{prop:extensions}
  Let \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\) be as just discussed.
  Let \(Y\) and \(Y'\) be the objects in the standard heart corresponding to \(\beta\) and \(\beta'\) respectively.
\begin{itemize}
\item if \(\alpha\) and \(\alpha'\) are not pointed, then we have extensions
  \[0 \to X' \to Y \to X \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X' \to 0.\]
\item if \(\alpha\) and \(\alpha'\) are crossing, then we have an extension
  \[0 \to X' \to (Y \oplus Y') \to X \to 0.\]
\end{itemize}
\end{proposition}
\begin{proof}
  The proof is once again a consequence of analysing the extensions explicitly via the complexes from the Khovanov--Seidel reconstruction.
  We do not reproduce the proof here, as the argument is contained in the proof of Theorem 5.5 in~\cite{tho:06}.
  (See also~\cite[Figure 4]{tho:06}.)
\end{proof}
Note that if we write down the relations in the Grothendieck group of our category that correspond to the extensions from each case of~\cref{prop:extensions}, then we obtain precisely the linear dependences that appear between the \(g\)-vectors in~\cref{lem:linearDependences}.
More precisely, we have that
\begin{itemize}
\item if \(\alpha\) and \(\alpha'\) are not pointed, then
  \([Y] = [X] + [X'] = [Y']\),
  from which we see \([X] + [X'] = ([Y] + [Y'])/2\);
\item if \(\alpha\) and \(\alpha'\) are crossing, then
  \([X] + [X'] = [Y] + [Y'].\)
\end{itemize}
This suggests that there should be a way to construct the \(g\)-vectors categorically in such a way that the \(g\)-vectors also map to the Grothendieck group of the category.
At the moment, we do not have a concise construction of the \(g\)-vectors purely categorically, and it would be interesting to find this.

>>>>

Recall from~\cref{rem:incompatibility-deg} that two arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.
Recall from~\cref{prop:uerp} the arcs \(\beta\) and \(\beta'\) associated to \(\alpha\) and \(\alpha'\).
Finally, recall from~\cref{lem:linearDependences} that the \(\b{g}\)-vectors of the arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
Let us interpret this dependince categorically.

Let \(X\) and \(X'\) be spherical objects in the standard heart that correspond to \(\alpha\) and \(\alpha'\) respectively.
First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial extension between the corresponding objects of the standard heart.
Next, let us understand~\(\beta\) and \(\beta'\) categorically.
\begin{proposition}\label{prop:extensions}
  Let \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\) be as just discussed.
  Let \(Y\) and \(Y'\) be the objects in the standard heart corresponding to \(\beta\) and \(\beta'\) respectively.
\begin{itemize}
\item if \(\alpha\) and \(\alpha'\) are not pointed, then we have extensions
  \[0 \to X' \to Y \to X \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X' \to 0.\]
\item if \(\alpha\) and \(\alpha'\) are crossing, then we have an extension
  \[0 \to X' \to (Y \oplus Y') \to X \to 0.\]
\end{itemize}
\end{proposition}
\begin{proof}
  The proof is once again a consequence of analysing the extensions explicitly via the complexes from the Khovanov--Seidel reconstruction.
  We do not reproduce the proof here, as the argument is contained in the proof of Theorem 5.5 in~\cite{tho:06}.
  (See also~\cite[Figure 4]{tho:06}.)
\end{proof}
Note that if we write down the relations in the Grothendieck group of our category that correspond to the extensions from each case of~\cref{prop:extensions}, then we obtain precisely the linear dependences that appear between the \(\b{g}\)-vectors in~\cref{lem:linearDependences}.
More precisely, we have that
\begin{itemize}
\item if \(\alpha\) and \(\alpha'\) are not pointed, then
  \([Y] = [X] + [X'] = [Y']\),
  from which we see \([X] + [X'] = ([Y] + [Y'])/2\);
\item if \(\alpha\) and \(\alpha'\) are crossing, then
  \([X] + [X'] = [Y] + [Y'].\)
\end{itemize}
This suggests that there should be a way to construct the \(\b{g}\)-vectors categorically in such a way that the \(\b{g}\)-vectors also map to the Grothendieck group of the category.
At the moment, we do not have a concise construction of the \(\b{g}\)-vectors purely categorically, and it would be interesting to find this.
